### 2019-09-11 scache/tii/tex/intro.tex
Fix the typo provided by JungleX

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
% Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
% Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, lineage of resilient distributed datasets (RDDs) in Spark\footnote{https://spark.apache.org/}, vertices and edges in Dryad \cite{dryad}, and Tez\footnote{https://tez.apache.org/}, etc.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, \textit{RDDs} in Spark\footnote{https://spark.apache.org/}, vertices in Dryad \cite{dryad}, etc.
Shuffle phase is always essential as communication between successive computation stages.
% Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=.85\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
% As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk.  
% And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
And the \textit{shuffle read} fetches intermediate results from remote disks through network. 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
Such task aggregation together with the coupled scheduling effectively simplifies task management.
% However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
However, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
% Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Moreover, since the shuffle read phase starts fetching data only after the corresponding reduce task starts, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
% Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
% Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
% As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
% To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as \textit{slow-start} from Hadoop MapReduce.
{\color{black}
% However, such early-start is by no means a panacea.
% This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% However, such early-start has several deficiencies.
% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
% Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

% {\color{black}
% We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
% The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
% We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
% }
% \begin{figure}
% 	\includegraphics[width=\linewidth]{fig/util}
% 	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
% 	\label{fig:util}
% 	\vspace{-1em}
% \end{figure}

>>>>

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
% Several sophisticated frameworks are used in industrial big data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
% Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, lineage of resilient distributed datasets (RDDs) in Spark\footnote{https://spark.apache.org/}, vertices and edges in Dryad \cite{dryad}, and Tez\footnote{https://tez.apache.org/}, etc.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, \textit{RDDs} in Spark\footnote{https://spark.apache.org/}, vertices in Dryad \cite{dryad}, etc.
Shuffle phase is always essential as communication between successive computation stages.
% Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=.85\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
% As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk.  
% And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
And the \textit{shuffle read} fetches intermediate results from remote disks through the network. 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
Such task aggregation together with the coupled scheduling effectively simplifies task management.
% However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
However, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
% Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Moreover, since the shuffle read phase starts fetching data only after the corresponding reduce task starts, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
% Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
% Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
% As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
% To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as \textit{slow-start} from Hadoop MapReduce.
{\color{black}
% However, such early-start is by no means a panacea.
% This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% However, such early-start has several deficiencies.
% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
% Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

% {\color{black}
% We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
% The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
% We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big data analysis by revealing the relationships between the various phases (Section \ref{model}).
% }
% \begin{figure}
% 	\includegraphics[width=\linewidth]{fig/util}
% 	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
% 	\label{fig:util}
% 	\vspace{-1em}
% \end{figure}

### 2019-09-11 scache/tii/tex/model.tex
Fix the typo provided by JungleX

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
The FRQ model use these overlaps to describe different scheduling strategies.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.

% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
Firstly, we introduces five input parameters of the FRQ model:
}
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

@@

% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap the shuffle phase and the map phases. We implemented this idea with SCache.
Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} show the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
This scheduling strategy avoids the I/O resource being idle in the map phase.
According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

>>>>

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
The FRQ model uses these overlaps to describe different scheduling strategies.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.

% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
Firstly, we introduce five input parameters of the FRQ model:
}
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

@@

% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap the shuffle phase and the map phases. We implemented this idea with SCache.
Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} show the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
SCache also overlaps the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
This scheduling strategy avoids the I/O resource being idle in the map phase.
According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

### 2019-09-11 scache/tii/tex/optimization.tex
Fix the typo provided by JungleX

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve shuffle optimization. 
{\color{blue}
Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
And we propose the pre-scheduling and pre-fetching to hide shuffle overhead into multi-round map tasks.
Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
}

@@

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce phase.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, the shuffle data transfer introduces an explicit overhead during shuffle read.
Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
Furthermore, because all reduce tasks start shuffle read simultaneously, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.

@@

SCache takes over all shuffle data and keep them on the memory instead of storing on disk liked the DAG frameworks.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

@@

\subsubsection{Problem of Random Mapping}\label{randomassign}
{\color{blue}
% Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
The performance of random mapping drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly mapping also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
}
% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

The job uses the Spark RangePartitioner and introduce an extreme high data skew.
Due to the extreme high data skew introducing by the partition, linear regression model cannot fit the result well.

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}
% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

>>>>

\section{Shuffle Optimization}
\label{opt}
This section presents detailed methodologies to achieve shuffle optimization. 
{\color{blue}
Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
And we propose the pre-scheduling and pre-fetching to hide shuffle overhead in multi-round map tasks.
Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
}

@@

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, the shuffle data transfer introduces an explicit overhead during shuffle read.
Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
Furthermore, because all reduce tasks start shuffle read simultaneously, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.

@@

SCache takes over all shuffle data and keeps them on the memory instead of storing on disk liked the DAG frameworks.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

@@

\subsubsection{Random Mapping Problem}\label{randomassign}
{\color{blue}
% Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
The performance of random mapping drops as the round number grows. 
This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
}
% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

The job uses the Spark RangePartitioner and introduces an extremely high data skew.
Due to the extremely high data skew introducing by the partition, the linear regression model cannot fit the result well.

@@

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}
% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

### 2019-09-11 scache/tii/tex/relatedwork.tex
Fix the typo provided by JungleX

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

\textbf{Industrial big-data.}
% In the \textit{Industry 4.0} which leading by the German Government, industrial big-data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
Industrial big-data refers to huge time-series data generated by industrial equipment in smart factories.
More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
Nowadays, the real challenge of big-data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
Several distributed computing frameworks become efficient tools in industrial big-data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
}

>>>>

{\color{black}
\textbf{Modeling.} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

\textbf{Industrial big data.}
% In the \textit{Industry 4.0} which leading by the German Government, industrial big data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
}
